### 2009-09-16 latex/paper1/contents.tex
paper

$$
f_v(w) = 1 + degree(w) \cdot (1 + \alpha), if module(w) = module(v)
, 1 + degree(w), otherwise
$$

@@

\begin{figure*}[!t]
\centering
\includegraphics[width=1.0\textwidth]{triads}
\caption{Triads (id vs. graph. reprs.)}
\label{fig:triads}
\end{figure*}

@@

\textbf{Software networks}. We have collected 65 software systems written in
Java, with size ranging from 111 to 35,363 classes. Java was chosen for being a
popular programming language in which many open source systems have been
written. The software networks, representing dependencies between classes, were
extracted with the tool Dependency Finder CITE.

>>>>

$$
f_v(w) = \left\{
\begin{array}{ll}

1 + degree(w) \cdot (1 + \alpha) &  \mathrm{if}\ module(w) = \\%= module(v) \\
                                 &  = module(v) \\
1 + degree(w) & \mathrm{otherwise}
\end{array}
\right.
$$

@@

\begin{figure*}[!t]
\centering
\includegraphics[width=1.0\textwidth]{triads}
\caption{The 13 network triads.}
\label{fig:triads}
\end{figure*}

@@

\textbf{Software networks}. We have collected 65 software systems written in
Java, with size ranging from 111 to 35,363 classes. Java was chosen for being a
popular programming language in which many open source systems have been
written. The software networks, representing dependencies between classes, were
extracted with the tool Dependency Finder\footnote{Available at
\url{http://depfind.sf.net}.}.
